---
title: "RExercise#2_Denola"
author: "Gem Dale G Deñola"
date: "2026-09-30"
output: html_document
---

```{r}
a <- 17
b <- 5

a + b
a - b
a * b
a / b
```

```{r}
a %% b
a %/% b
```

```{r}
2^10
```

#Question 1 
```{r}
17/5 
17%%5
17%/%5

```
# They relate each other in a way, that function differently. The divide algorithm counts the whole number including the decimal meanwhile the modulo, counts the remainder and for the mix divide and modulo it presents 3 because it computes it into a whole number rather than with a decimal or the remainder.

```{r}
10%%3 
10%/%3 
```
# this calculates the Remainder. 1 is the remainder
# this computes for the whole number. 3 is the result

#Part B
```{r}
x <- 42 
y <- 42L
z <- "42"
w <- TRUE
v <- 3 + 2i

typeof(x)
typeof(y)
typeof(z)
typeof(w)
typeof(v)
```
#class
```{r}
class(x)
class(y)
class(z)
class(w)
class(y)
```
#mode
```{r}
mode(x)
mode(y)
mode(z)
mode(w)
mode(v)
```
#Question 3
```{r}
x <- 42
y <- 42L

```
# They are different because "x <- 42" automatically makes it a double type. Meanwhile y <- 42L reassigns the value to be integer.

#Question 4

#typeof()
#class()
#mode()
# Each has different functions and to identify an object. For instance "intege" for typeof() and "numeric for mode() and "factor class().

#Part C
```{r}
num_string<- "123"
as.numeric(num_string)
as.logical(num_string)
```

```{r}
as.logical(0)
as.logical()
```

```{r}
bad_string <- "hello123"
```
#Question 5

# It issues a warning instead of crashing it because R allows data to process and to continue to run smoothly without encountering malformed values.

# Ignoring these warnings can corrupt the value and caculations and results.

#Question 6
```{r}
as.logical(2)
as.logical(-1)
```
# I think it will produce both TRUE value.
# R only reads 0 as a FALSE number anything above and under is TRUE. 

#Part D
```{r}
first_name <- "Juan"
last_name <- "Dela Cruz"
print(first_name)
print(last_name)
```

```{r}
first_name <- "Juan"
last_name <- "Dela Cruz"
paste(first_name, last_name)
paste0(first_name, last_name)
```

```{r}
paste(first_name, last_name, sep = "-")
```

```{r}
full_name <- paste0(first_name, last_name, sep = "-")
age <- 21
paste0(full_name, "is", age, "years old.")
```
#Question 7

#They produce different result because paste() there's a space automatically meanwhile paste0() produces none

#Question 8

#It didn't produce an error. paste0() automatically runs the type into character inputs into strings.

#Part E
```{}
"5" + 5 
# non-numeric argument to binary operator
```

```{r}
5 + 5 
```

Question 9

# It runs with an error to ensure data isn't corrupted or unexpected results. This also protects data by not running it.


Question 10

# 


